Mental Health Plays Significant Role in Physical Wellness in 1972 to 2022 US General Social Surveys

### 2024-04-18 paper/paper.qmd
update paper and code stylying

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \beta_0 + \beta_1 days + \beta_2 diagnosis\\
\beta &\sim \mbox{Normal}(0, 2.5) 
\end{align}

@@

@@

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

@@

>>>>

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \beta_0 + \beta_1 days + \beta_2 diagnosis\\
\beta_i &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

@@

Lastly, by posterior predictive check, the posterior distribution indicates that the model is not doing a good job of fitting the data. The check result could be due to limitations of data mentioned above; furthermore, adding more relevant variables to the linear regression equation could as well improve the strength of the model.

@@

In @fig-ppcheckandposteriorvsprior, we implement a posterior predictive check and compared the posterior with the prior. By definition, the posterior should be able to be used to simulate data similar to the actual data; however, the posterior simulated data barely recollect the characteristic of the dataset from GSS. This means that the model lack of strength in terms of the relationship. The weakness could be a result of data limitations mentioned in [Discussion].

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "The Model Fits Barely to the Data, Hinting A Weak Model for Explaining the circumstances"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

@@

@fig-stanareyouokay-1 is a trace plot. It shows lines bouncing around horizontally and have a nice overlap between the chains. @fig-stanareyouokay-2 is a Rhat plot. From the plot, $\hat{R} = 1.05$, which is very close to 1, and ideally no more than 1.1.  These results suggest no problems in model we built for our paper.

@@

\newpage
\break
